|

### 2021-06-22 documentation/paper.Rmd
Fix add_pm and add_pm_party functions, recompile mini data and recompile paper

# Get conditional effects

cond_fx <- 
  conditional_effects(
    death_mod,
    "deaths",
    conditions =
      tibble(
        time = seq(2, 14, by = 6),
        cond__ = c("Mar. 2020", "Sep. 2020", "Mar. 2021")
      )
  )$deaths

@@

cond_fx %>% 
  ggplot(
    aes(
      x = deaths,
      y = estimate__,
      ymin = estimate__ - qnorm(.975)*se__,
      ymax = estimate__ + qnorm(.975)*se__
    )
  ) +
  facet_wrap(~ cond__) +
  geom_vline(
    xintercept = 0,
    colour = britpol:::bailey_colours("grey4"),
    linetype = "dotted"
  ) +
  geom_ribbon(
    colour = NA,
    fill = britpol:::bailey_colours("red"),
    alpha = .2) +
  geom_line(colour = britpol:::bailey_colours("red")) +
  scale_y_continuous(
    breaks = seq(-.1, .1, by = .05),
    labels = scales::percent_format(suffix = "pts", accuracy = 1)
  ) +
  scale_x_continuous(
    breaks = seq(-10, 10, by = 5),
    labels = scales::number_format(scale = 100)
  ) +
  coord_cartesian(
    ylim = c(-.1, .1),
    xlim = c(-10, 10)
  ) +
  labs(
    y = "Change in Con. Support, Past 4 Weeks",
    x = "Change in Deaths Attributable to COVID-19, Past 4 Weeks"
  ) +
  theme_bailey()
```

>>>>

cond_fx <- 
  conditional_effects(
    death_mod,
    "deaths",
    conditions =
      tibble(
        time = round(seq(3, 18, length.out = 3), 0),
        cond__ = 
          as_date("2019-12-12") %m+%
          months(time) %>% 
          format("%b. %Y")
      )
  )$deaths

@@

cond_fx %>% 
  ggplot(
    aes(
      x = deaths,
      y = estimate__,
      ymin = estimate__ - qnorm(.975)*se__,
      ymax = estimate__ + qnorm(.975)*se__
    )
  ) +
  facet_wrap(~ cond__) +
  geom_vline(
    xintercept = 0,
    colour = britpol:::bailey_colours("grey4"),
    linetype = "dotted"
  ) +
  geom_ribbon(
    colour = NA,
    fill = britpol:::bailey_colours("red"),
    alpha = .2) +
  geom_line(colour = britpol:::bailey_colours("red")) +
  scale_y_continuous(
    breaks = seq(-.1, .1, by = .05),
    labels = scales::percent_format(suffix = "pts", accuracy = 1)
  ) +
  scale_x_continuous(
    breaks = seq(-10, 10, by = 5),
    labels = scales::number_format(scale = 100)
  ) +
  coord_cartesian(
    ylim = c(-.1, .1),
    xlim = c(-10, 10)
  ) +
  labs(
    y = "Change in Con. Support, Past 4 Weeks",
    x = "Change in Deaths Attributable to COVID-19, Past 4 Weeks"
  ) +
  theme_bailey()
